Supporting information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2017-02-03 docs/response.tex

    Thank you for the helpful suggestion of subheadings to clarify the
    organization of our results: we added subheadings to distinguish
    global, regional, country-level model projections, along with
    uncertainty analysis of vaccine characteristics and sensitivity
    analysis.  We have also added the following sentences in the
    regional projections section:
    \begin{quoting}
      The UNAIDS targets based on antiviral treatment affect the
      number of PLHIV by prolonging survival (which increases PLHIV
      compared to status quo) and by reducing transmission (which
      decreases PLHIV). By contrast, vaccination averts new
      infections, reducing PLHIV without the concomitant improvement
      in survival.  This transmission reduction achieved by
      vaccination is greater in African regions that have a high
      incidence, including Swaziland, Uganda, and South Africa, than
      in Asian countries with lower incidence, such as India (Figure
      2).
    \end{quoting}

    \begin{original}
      5. It was not clear how long it would take to vaccinate
      a fully immunized individual, and the optimal age group. It
      would have helped to have a brief summary of the vaccine's
      target product profile (TPP).
    \end{original}

    Following this suggestion as well as the details provided for
    inclusion by Reviewer \#3, we added a description of the target
    product profile from the HVTN 100/702 trials and expanded the
    description of the most recent vaccine candidate in the context of
    its predecessor:
    \begin{quoting}
      For example, the phase III RV144 trial in Thailand of an
      ALVAC-HIV/gp120 regimen demonstrated efficacies of 60.5\% after
      1 year and of 31.2\% after 3.5 years among participants aged 18
      to 30 years, with vaccine doses administered at weeks 0, 4, 12,
      and 24 (9). Results of the HVTN 100 trial in South Africa,
      which used an updated ALVAC-HIV/gp120 regimen, showed a more
      robust immune response than RV144 in participants aged 18 to 40
      (10).  Given the safety and immunogenicity demonstrated by HVTN
      100, the HVTN 702 study was initiated in November 2016 to
      determine HIV vaccine efficacy in 14 sites across South Africa
      (11). The trial is enrolling 18 to 35 year olds with vaccination
      scheduled at months 0, 1, 3, 6, and 12 (12).  Other advances in
      research on HIV vaccines have included candidates based on
      adenovirus vectors (13).  Motivated by strong pre-clinical
      scientific underpinnings (14), three phase I/II trials have been
      initiated as part of the Ad26/MVA/trimer gp140 program and an
      efficacy study is planned for later in 2017 (15).  In addition,
      investigation into the prophylactic potential of broadly acting
      neutralizing antibodies has provided preliminary evidence for
      enhanced viral clearance through immunotherapy (16).
    \end{quoting}

@@

    \begin{original}
      6. Finally I thought it might be helpful to briefly discuss the
      implications of other partially protective vaccines. More and
      more we're seeing new vaccines come online, which do not have
      the high levels of protection we associate with say measles
      vaccine. For example, in addition to HIV, there's the next
      generation TB, malaria, and other parasite vaccines—increasingly
      such vaccines will not replace existing drug therapies but
      instead will be used alongside them—sometimes called
      ``vaccine-linked chemotherapy''. The analysis here emphasizes
      why and how vaccine-linked chemotherapy can be successfully
      modeled and applied and that should be mentioned.
    \end{original}

    Thank you for this excellent suggestion. In the second paragraph
    of the introduction, we have added:
    \begin{quoting}
      Likewise, at the frontier of vaccinology for myriad other
      diseases, including malaria, TB, hookworm, and dengue, is the
      development of partially efficacious vaccines (17--19). In cases
      where vaccines may not alone be sufficient for disease
      elimination, they may nonetheless be a component of disease
      control in combination with drug therapies. Here we evaluate
      such vaccine-linked chemotherapy approaches (20) for HIV.
    \end{quoting}

@@

    \section{Reviewer \#3}
    \begin{original}
      Suitable Quality?: Yes\\
      Sufficient General Interest?: Yes\\
      Conclusions Justified?: Yes\\
      Clearly Written?: Yes\\
      Procedures Described?: Yes\\
      Supplemental Material Warranted?: Yes

      Medlock and colleagues describe an infectious disease modeling
      approach to evaluating the impact of HIV vaccines of varying
      degrees of efficacy and global coverage to the global HIV
      pandemic. The paper is concise and well written. The conclusions
      are within the scope of stated limitations of the approach. This
      paper will be of much interest to the field and will be cited by
      many in the HIV vaccine field. Coming at a time of growing
      HIV/AIDS complacency, it's timing couldn't be better. Attention
      to the points below would strengthen the manuscript.

      1. The authors should add a sentence or two describing other HIV
      prevention modalities, such as adult medical male circumcision,
      PrEP, antibody mediated protection, and treatment as prevention,
      that will likely join an effective HIV vaccine as tools to
      mitigate HIV transmission.
    \end{original}

    We have added the following to the discussion section:
    \begin{quoting}
      The vaccination and treatment as prevention approaches
      considered here would be complementary to other HIV prevention
      modalities, such as adult medical male circumcision (31),
      pre-exposure prophylaxis (PrEP, 32) and antibody-mediated
      protection (33). The combination of these interventions is
      likely to have synergistic effects on mitigating HIV
      transmission.
    \end{quoting}

@@

    \begin{original}
      2. While HVTN 100 was an important study, and the final safety
      and immunogenicity study of ALVAC vCP2348 + gp120 bivalent C
      that led to the decision to launch the HVTN 702 HIV vaccine
      efficacy study, it is the latter study that is more relevant to
      the authors' thesis. HVTN 702 started in mid-November 2016; it
      was highlighted in many 01 December 2016 World AIDS Day
      announcements. This is the first HIV efficacy study to launch in
      seven years and builds on the success of the only HIV vaccine
      efficacy study that showed efficacy, RV 144, which the authors
      cite, but they need to connect HVTN 702 to RV 144 and HVTN 100
      to complete the historical and scientific context.
    \end{original}

    Thank you for this important context.  We have provided more
    context to connect the RV 144, HVTN 100, and the HVTN 702 trials,
    as suggested, in the introduction:
    \begin{quoting}
      For example, the phase III RV144 trial in Thailand of an
      ALVAC-HIV/gp120 regimen demonstrated efficacies of 60.5\% after
      1 year and of 31.2\% after 3.5 years among participants aged 18
      to 30 years, with vaccine doses administered at weeks 0, 4, 12,
      and 24 (9). Results of the HVTN 100 trial in South Africa,
      which used an updated ALVAC-HIV/gp120 regimen, showed a more
      robust immune response than RV144 in participants aged 18 to 40
      (10).  Given the safety and immunogenicity demonstrated by HVTN
      100, the HVTN 702 study was initiated in November 2016 to
      determine HIV vaccine efficacy in 14 sites across South Africa
      (11). The trial is enrolling 18 to 35 year olds with vaccination
      scheduled at months 0, 1, 3, 6, and 12 (12).
    \end{quoting}

@@

    \begin{original}
      3. While HIV vaccine development based on ALVAC + gp120 products
      are mentioned in the manuscript, the other major effort in the
      field, the Ad26/MVA/trimer gp140 program is not. This should be
      corrected. The Ad26 program has strong pre-clinical scientific
      underpinnings that have supported advancement into phase I/II
      studies with a first phase IIb efficacy study planned for summer
      2017. While the authors do note that protein immunogens designed
      to elicit broad and potent neutralizing antibody against the
      HIV-1 envelope protein are being explored, they are in much
      earlier clinical development than either the ALVAC + gp120 or
      Ad26 programs.
    \end{original}

    We have revised the introduction to reference both efforts
    involving broadly neutralizing antibodies and contributions to
    date of the Ad26/MVA/trimer gp140 program:
    \begin{quoting}
      Other advances in HIV vaccine research have included candidates
      based on adenovirus vectors (13). Motivated by strong
      pre-clinical scientific underpinnings (14), three phase I/II
      trials have been initiated as part of the Ad26/MVA/trimer gp140
      program and an efficacy study is planned for later in 2017
      (15). In addition, investigation into the prophylactic potential
      of broadly acting neutralizing antibodies has provided
      preliminary evidence for enhanced viral clearance through
      immunotherapy (16).
    \end{quoting}
